Data cleaning for mass mobiliziation data version

### 2023-07-01 Output/Submission files/manuscript_anon_v2.Rmd
Copyedits to appendix (e.g. shortening tables)

model.size.base2 <- glmmTMB::glmmTMB(max_size ~ jucon.1lag + legcon.1lag + osorg.1lag + altinf.1lag + libdem.1lag  + natlpartyorg.lag + v2elirreg.inv +  +   winner.share.upd*v2elirreg.inv  + presidential + inc.termlimit.num  +  physinteg.1lag + physintlag.sq + urban.pct + rentierstate + taxstate + n.events.pre + unscheduled_election + regional_success_lag ,
                                ziformula=~.,
                                data = nelda2.sub %>% filter(inc.lose == "0"),
                                family=truncated_nbinom2)
summary(model.size.base2)

>>>>

model.size.base2 <- glmmTMB::glmmTMB(max_size ~ jucon.1lag + legcon.1lag + osorg.1lag + altinf.1lag + libdem.1lag  + natlpartyorg.lag + v2elirreg.inv + gdpgro.1lag  +   winner.share.upd*v2elirreg.inv  + presidential + inc.termlimit.num  +  physinteg.1lag + physintlag.sq + urban.pct + rentierstate + taxstate + n.events.pre + unscheduled_election + regional_success_lag ,
                                ziformula=~.,
                                data = nelda2.sub %>% filter(inc.lose == "0"),
                                family=truncated_nbinom2)
summary(model.size.base2)

### 2023-07-01 Output/appendix_v4.Rmd
Copyedits to appendix (e.g. shortening tables)

## Repression and pre-election protest

The main analysis already controls for possible confounding by the state's repressive capacity; i.e. the possibility that in highly repressive states, protest is deterred and fraud can proceed unopposed. However, it may still be useful to check an alternative explanation\textemdash perhaps protest is deterred in highly repressive states with considerable pre-election unrest (that is, when protest appears to be exceeding the ability of the state to contain). To check this possibility, a variation of Model 1 from the main text is run, but with an interaction between the number of pre-election protests and the lagged *physical integrity* variable. If protest risk deters manipulation in this way, there should be a negative and significant effect for the number of pre-election protests in highly repressive states. Figure \@ref(fig:prot-rep-fraud) shows the absence of such an effect. In fact, there is no significant difference in the predicted level of fraud at lower levels of physical integrity, even when pre-election protest is widespread. A significant effect is seen at the high end of protection of physical integrity rights, but it is present only in extreme cases\textemdash the value of pre-election protests chosen here, 25, is above the 98th percentile for the variable\textemdash and is in the opposite direction predicted by this counterargument. That is, more numerous pre-election protest is associated with higher predicted levels of fraud in less repressive states than when the pre-election period is quiet. This robustness check shows that protest in a repressive environment does not appear to deter fraud, and supports the view that manipulation may be used to attempt to claim a large margin of victory or to prevent elite or bureaucratic splits in a challenging period.

@@

## Prior manipulation

@@

```{r table-lagged-manip, results='asis', echo=FALSE}
models3 <- list()
models3[['Model 5']] <- model.n.base2.lag
models3[['Model 6']] <- model.d.base2.lag
models3[['Model 7']] <- model.size.base2.lag

t4a <- huxreg(models3, tidy_args = c("component" = "cond"), borders = 0, number_format = 2,  omit_coefs = c("sd__(Intercept)", "sd__Observation"), coefs = c("Intercept" = "(Intercept)", "Judicial ind. (lag)" = "jucon.1lag", "Liberal democracy index" = "libdem.1lag",
            "Legislative constraints (lag)" = "legcon.1lag", "Alternative info. (lag)" = "altinf.1lag",                             "GDP growth rate (lag)" = "gdpgro.1lag",                               "Civil society openness (lag)" = "osorg.1lag", "National party organization (lag)" = "natlpartyorg.lag", "Presidential" = "presidential", "Incumbent term-limited" = "inc.termlimit.num",
            "Physical integrity (lag)" = "physinteg.1lag", "Phys. int. (lag) squared" = "physintlag.sq", "Number of pre-election protests" = "n.events.pre", "Off-schedule election" = "unscheduled_election", "Regional protest diffusion" = "regional_success_lag"),
              statistics = character(0)) %>% set_caption("Table XX: Models of number, duration, and size of protests") %>% insert_row("", "Number", "Duration", "Size", after = 0)
theme_compact(t4a, header_rows = TRUE, header_cols = FALSE)

t4b <- huxreg(models3, tidy_args = c("component" = "cond"), borders = 0, number_format = 2,  omit_coefs = c("sd__(Intercept)", "sd__Observation"), coefs = c("Change in election fraud" = "fraud.change", "Winner vote-share" = "winner.share.upd", 
            "Urban" = "urban.pct", "Rentier state" = "rentierstate", "Tax state" = "taxstate", "Change in fraud : Winner vote-share" = "fraud.change:winner.share.upd"),
              statistics = character(0)) %>% set_caption("Table XX: Models of number, duration, and size of protests") %>% insert_row("", "Number", "Duration", "Size", after = 0)
theme_compact(t4b, header_rows = TRUE, header_cols = FALSE)

@@

## Chosen successors

The models in the main text control for the presence of term-limited executive incumbents, based on the logic in Hale [@hale_patronal_2014]. However, it could be the case that the nature of a term-limited election affects the behavior of protesters and election manipulators alike; that is, perhaps when there is a designated successor, the heir apparent is better able to mobilize the resources of the state to manipulate elections and suppress protest. Using a variable from NELDA that codes for designated successors, the following models add a categorical variable for the incumbent's status, which can take on the following values: *executive eligible*, *chosen successor*, *contested executive election*, and *legislative election*. As Table \@ref(tab:successor-table) and Figure \@ref(fig:successor-fig) show, the results are largely similar to those in the main text. Higher levels of fraud does make the occurrence of protest more likely at low incumbent vote-shares, but this does not translate into a higher risk of more numerous or larger protest events.

@@

models4 <- list()
models4[['Model 5']] <- model.n.base2.succ
#models4[['Model 6']] <- model.d.base2.hurd
models4[['Model 6']] <- model.size.base2

t5a <- huxreg(models4, tidy_args = c("component" = "cond"), borders = 0, number_format = 2,  omit_coefs = c("sd__(Intercept)", "sd__Observation"), statistics = character(0)) %>% set_caption("Models of number and size of protests") %>% insert_row("", "Number", "Size", after = 0)
theme_compact(t5a, header_rows = TRUE, header_cols = FALSE)

@@

## Including liberal democracies

@@

```{r lib-table, echo=FALSE}

@@

t6a <- huxreg(models5, tidy_args = c("component" = "cond"), borders = 0, number_format = 2,  omit_coefs = c("sd__(Intercept)", "sd__Observation"), statistics = character(0)) %>% set_caption("Table XX: Models of number and size of protests, inclu. liberal democracies") %>% insert_row("", "Number", "Size", after = 0)
theme_compact(t6a, header_rows = TRUE, header_cols = FALSE)
```

@@

models <- list()
models[['Model 10']] <- m1

modelsummary(models, stars = T,  title = 'Random-intercept multilevel model of overall election integrity',
             coef_rename = 
               c("jucon.1lag" = "Judical independence (lag)", "legcon.1lag" = "Leg. constraints (lag)", 
                 "gdpgro.1lag" = "GDP growth rate (lag)", "altinf.1lag" = "Alternative info. (lag)", 
                 "osorg.1lag" = "Civil soc. openness (lag)", "econ.crisis.nelda.1lag1" = "Economic crisis", 
                 "natlpartyorg.lag" = "National party organization (lag)", "presidential1" = "Presidential election",
                 "inc.termlimit.num" = "Incumbent term-limited", "libdem.1lag" = "Liberal democracy index (lag)", 
                 "urban.pct" = "Urbanization", "rentierstate" = "Rentier state", "taxstate" = "Tax state",
                 "n.events.massmob.pre" = "Number of pre-election protests", "median.participants.mm.pre" = "Median size of pre-election protests"))
```

@@

```{r models-hurdle-fulldv, warning = FALSE, message = FALSE, include = F}
model.n.base2.elfr <- glmmTMB::glmmTMB(n.events.post ~  jucon.1lag + legcon.1lag + gdpgro.1lag + altinf.1lag + pubseccorrup.lag + osorg.1lag + econ.crisis.nelda.1lag + natlpartyorg.lag + v2xel_frefair + pubseccorrup.lag +    winner.share.upd*v2xel_frefair  + presidential + inc.termlimit.num  +  physinteg.1lag + physintlag.sq + urban.pct + rentierstate + taxstate + n.events.pre + unscheduled_election +  inc.lose,
                                          zi = ~.,
                                          family= nbinom2,
                                          data = nelda2.sub)
summary(model.n.base2.elfr)

@@

nelda2.sub <- nelda2.sub %>% mutate(surv_status = ifelse(d.events.num > 0, 1, NA))
km <-  with(nelda2.sub, Surv(d.events.num, surv_status))

cox2.elfr <- coxph(Surv(d.events.num, surv_status) ~ jucon.1lag + legcon.1lag + altinf.1lag +  osorg.1lag + gdpgro.1lag + natlpartyorg.lag + winner.share.upd*v2xel_frefair  + presidential + inc.termlimit.num  +  physinteg.1lag + physintlag.sq + urban.pct + rentierstate + taxstate + n.events.pre + unscheduled_election +  as.factor(inc.lose), data = nelda2.sub %>% filter(d.events.num > 0 & inc.replaced.prot == 0))
summary(cox2.elfr)

@@

Moving to the hurdle models of post-election protest, we do not observe much of a relationship between overall election integrity and protest. There is no statistically significant relationship between election integrity and protest occurrence in Model 2. Neither is there any significant relationship in interaction with the winner's vote-share, as shown in Figure \@ref(fig:b-protests-margin), or with economic crisis, as in Figure \@ref(fig:b-protests-crisis). The coefficient on the interaction term for public sector corruption and overall election integrity is statistically significant, though there is no significant effect at typical values for covariates and election integrity (as shown in Figure \@ref(fig:b-protests-corrupt)).

In the corresponding results for the number of post-election protests, there is similarly muted evidence for a connection between the overall level of manipulation and protest risk to incumbents. There is no significant difference between the marginal effect of common levels of election integrity on the number of post-election protests for typical cases across any margin of victory (Figure \@ref(fig:n-protests-margin)). During an economic crisis, *cleaner* elections are associated with an increase in the number of protests (\@ref(fig:n-protests-crisis)). This is plausibly due to the crisis weakening both the government's ability to generate manipulation [@greene_why_2007] and its ability to co-opt or put down the protests. Finally, public sector corruption is associated with a significant increase in the marginal effect of poor-integrity elections on protest\textemdash but only when the corruption measure is at its maximum (Figure \@ref(fig:n-protests-corrupt)).

As a whole, the results are in accordance with the theory proposed in the main paper. There is no consistent evidence that lower-quality elections are associated with either a higher risk of protest initiation, or with a larger number of post-election protests.

```{r zero-model-table-fulldv, echo=FALSE, results='asis'}

models <- list()
#models[['Model XXa']] <- model.n.base2.elfr
models[['Model XXb']] <- model.size.base2.elfr
models[['Model XXc']] <- cox2.elfr

modelsummary::modelsummary(models, coef_omit = "(Intercept)", longtable=T, stars = T, title = 'Hurdle models of post-election protest (counts)',
                           coef_rename = 
               c("count_(Intercept)" = "Intercept", "count_jucon.1lag" = "Judical independence (lag)", "count_legcon.1lag" = "Leg. constraints (lag)", 
                 "count_gdpgro.1lag" = "GDP growth rate (lag)", "count_altinf.1lag" = "Alternative info. (lag)", 
                 "count_osorg.1lag" = "Civil soc. openness (lag)", "count_econ.crisis.nelda.1lag1" = "Economic crisis", 
                 "count_natlpartyorg.lag" = "National party organization (lag)", "count_presidential1" = "Presidential election",
                 "count_inc.termlimit.num" = "Incumbent term-limited",  
                 "count_urban.pct" = "Urbanization", "count_rentierstate" = "Rentier state", "count_taxstate" = "Tax state",
                 "count_n.events.massmob.pre" = "Number of pre-election protests", "count_pubseccorrup.lag" = "Public sector corruption (lag)", "count_v2xel_frefair" = "Election integrity",
                 "count_physinteg.1lag" = "Physical integrity (lag)", "count_physintlag.sq" = "Physical integrity (lag), squared", "count_winner.share.upd" = "Incumbent vote-share", "v2elirreg.inv" = "Election fraud",  "winner.share.upd" = "Incumbent vote-share",  "v2xel_frefair" = "Election integrity"))

@@

```{r n-protests-duration-sim, echo=FALSE, message=FALSE}
Sim1 <- coxsimInteract(cox2.elfr, b2 = "v2xel_frefair", b1 = "winner.share.upd", qi = "Hazard Ratio", X2 = c(-.4, 1.7),  X1 = seq(0.01, 1, by = .01), nsim = 2000)
p.duration.margin <- simGG(Sim1)
p.duration.margin <- p.duration.margin + labs(x = "Incumbent vote-share", y = "Hazard ratio" , title = "Hazard ratios for protest termination")  + theme_bw()
```

@@

```{r n-protests-duration-fulldv, fig.cap="Election integrity, incumbent vote-share, and duration of protest events", echo=FALSE, out.width = '70%', fig.align='center'}
p.duration.margin #Hazard ratios > 1 indicate an increased risk of termination of protest wave. So worse elections are associated with quicker demise of protest waves among cases where protest occurred and incumbents were not replaced.
```

>>>>

# Repression and pre-election protest

The main analysis already controls for possible confounding by the state's repressive capacity; i.e. the possibility that in highly repressive states, protest is deterred and fraud can proceed unopposed. However, it may still be useful to check an alternative explanation\textemdash perhaps protest is deterred in highly repressive states with considerable pre-election unrest (that is, when protest appears to be exceeding the ability of the state to contain). To check this possibility, a variation of Model 1 from the main text is run, but with an interaction between the number of pre-election protests and the lagged *physical integrity* variable. If protest risk deters manipulation in this way, there should be a negative and significant effect for the number of pre-election protests in highly repressive states.

Figure \@ref(fig:prot-rep-fraud) shows the absence of such an effect. In fact, there is no significant difference in the predicted level of fraud at lower levels of physical integrity, even when pre-election protest is widespread. A significant effect is seen at the high end of protection of physical integrity rights, but it is present only in extreme cases\textemdash the value of pre-election protests chosen here, 25, is above the 98th percentile for the variable\textemdash and is in the opposite direction predicted by this counterargument. That is, more numerous pre-election protest is associated with higher predicted levels of fraud in less repressive states than when the pre-election period is quiet. This robustness check shows that protest in a repressive environment does not appear to deter fraud, and supports the view that manipulation may be used to attempt to claim a large margin of victory or to prevent elite or bureaucratic splits in a challenging period.

@@

# Prior manipulation

@@

```{r table-lagged-manip, results='asis', echo=FALSE, warning=FALSE}
models3 <- list()
models3[['Model 4']] <- model.n.base2.lag
models3[['Model 5']] <- model.d.base2.lag
models3[['Model 6']] <- model.size.base2.lag

t4a <- huxreg(models3, tidy_args = c("component" = "cond"), borders = 0, number_format = 2,  omit_coefs = c("sd__(Intercept)", "sd__Observation"), coefs = c("Intercept" = "(Intercept)", "Fraud change" = "fraud.change", "Incumbent vote-share" = "winner.share.upd", "Fraud change:Incumbent vote-share" = "fraud.change:winner.share.upd"),
              statistics = character(0)) %>% set_caption("Models of number, duration, and size of protests") %>% insert_row("", "Number", "Duration", "Size", after = 0) %>% insert_row("Controls", "Yes", "Yes", "Yes", after = 10)
theme_compact(t4a, header_rows = TRUE, header_cols = FALSE)  %>% set_bottom_border(10, everywhere)

@@

# Chosen successors

The models in the main text control for the presence of term-limited executive incumbents, based on the logic in Hale [@hale_patronal_2014]. However, it could be the case that the nature of a term-limited election affects the behavior of protesters and election manipulators alike; that is, perhaps when there is a designated successor, the heir apparent is better able to mobilize the resources of the state to manipulate elections and suppress protest. Using a variable from NELDA that codes for designated successors, the following models add a categorical variable for the incumbent's status, which can take on the following values: *executive eligible*, *chosen successor*, *contested executive election*, and *legislative election*. As Figure \@ref(fig:successor-fig) show, the results are largely similar to those in the main text. Higher levels of fraud does make the occurrence of protest more likely at low incumbent vote-shares, but this does not translate into a higher risk of more numerous or larger protest events.

@@

models4 <- list()
models4[['Model 7']] <- model.n.base2.succ
#models4[['Model 6']] <- model.d.base2.hurd
models4[['Model 8']] <- model.size.base2

t5a <- huxreg(models4, tidy_args = c("component" = "cond"), borders = 0, number_format = 2,  omit_coefs = c("sd__(Intercept)", "sd__Observation"), statistics = character(0)) %>% set_caption("Models of number and size of protests") %>% insert_row("", "Number", "Size", after = 0)
#theme_compact(t5a, header_rows = TRUE, header_cols = FALSE)

@@

# Including liberal democracies

@@

```{r lib-table, echo=FALSE, warning=FALSE}

@@

t6a <- huxreg(models5, tidy_args = c("component" = "cond"), borders = 0, number_format = 2,  omit_coefs = c("sd__(Intercept)", "sd__Observation"), coefs = c("Intercept" = "(Intercept)", "Election fraud" = "v2elirreg.inv", "Winner vote-share" = "winner.share.upd", "Election fraud : Winner vote-share" = "v2elirreg.inv:winner.share.upd"), statistics = character(0)) %>% set_caption("Models of number and size of protests, inclu. liberal democracies") %>% insert_row("", "Number", "Size", after = 0)
theme_compact(t6a, header_rows = TRUE, header_cols = FALSE)  %>% insert_row("Controls", "Yes", "Yes", after = 10) %>% set_bottom_border(10, everywhere)
```

@@

models <- list()
models[['Model 9']] <- m1

modelsummary(models, stars = T,  title = 'Random-intercept multilevel model of overall election integrity', gof_omit = "AIC|BIC",
             coef_rename = 
               c("jucon.1lag" = "Judical independence (lag)", "legcon.1lag" = "Leg. constraints (lag)", 
                 "gdpgro.1lag" = "GDP growth rate (lag)", "altinf.1lag" = "Alternative info. (lag)", "presidential" = "Presidential", "n.events.pre" = "N. of pre-election protest",
                 "physinteg.1lag" = "Physical integrity (lag)",
                 "physintlag.sq" = "Phys. integ. (lag), squared", "unscheduled_election" = "Off-schedule election",
                 "osorg.1lag" = "Civil soc. openness (lag)", "econ.crisis.nelda.1lag1" = "Economic crisis", 
                 "natlpartyorg.lag" = "National party organization (lag)", "presidential1" = "Presidential election",
                 "inc.termlimit.num" = "Incumbent term-limited", "libdem.1lag" = "Liberal democracy index (lag)", 
                 "urban.pct" = "Urbanization", "rentierstate" = "Rentier state", "taxstate" = "Tax state",
                 "n.events.massmob.pre" = "Number of pre-election protests", "median.participants.mm.pre" = "Median size of pre-election protests"))
```

@@

```{r models-hurdle-fulldv, warning = FALSE, message = FALSE, include = F}
model.n.base2.elfr <- glmmTMB(n.events.post ~ jucon.1lag + legcon.1lag + altinf.1lag + libdem.1lag + gdpgro.1lag +  + osorg.1lag  + natlpartyorg.lag +  v2xel_frefair*winner.share.upd   + presidential + inc.termlimit.num  +  physinteg.1lag + physintlag.sq + urban.pct + rentierstate + taxstate + n.events.pre + unscheduled_election + regional_success_lag,
                               ziformula=~.,
                              data = nelda2.sub %>% filter(inc.lose == "0"),
                                family=truncated_nbinom2)
summary(model.n.base2.elfr)

@@

model.n.griev.elfr <- glmmTMB::glmmTMB(n.events.post ~ jucon.1lag + legcon.1lag + gdpgro.1lag + altinf.1lag + libdem.1lag +  osorg.1lag +  natlpartyorg.lag + v2xel_frefair +  v2xel_frefair*gdpgro.1lag  + presidential + inc.termlimit.num  +  physinteg.1lag + physintlag.sq + urban.pct + rentierstate + taxstate + n.events.pre + unscheduled_election + regional_success_lag ,
                                ziformula=~.,
                                data = nelda2.sub %>% filter(inc.lose == "0"),
                                family=truncated_nbinom2)

model.size.base2.elfr <- glmmTMB::glmmTMB(max_size ~ jucon.1lag + legcon.1lag + osorg.1lag + altinf.1lag + libdem.1lag  + natlpartyorg.lag + v2xel_frefair + gdpgro.1lag  +   winner.share.upd*v2xel_frefair  + presidential + inc.termlimit.num  +  physinteg.1lag + physintlag.sq + urban.pct + rentierstate + taxstate + n.events.pre + unscheduled_election + regional_success_lag ,
                                ziformula=~.,
                                data = nelda2.sub %>% filter(inc.lose == "0"),
                                family=truncated_nbinom2)

model.size.griev.elfr <- glmmTMB::glmmTMB(max_size ~ jucon.1lag + legcon.1lag + gdpgro.1lag + altinf.1lag + libdem.1lag +  osorg.1lag +  natlpartyorg.lag + v2xel_frefair +  v2xel_frefair*gdpgro.1lag  + presidential + inc.termlimit.num  +  physinteg.1lag + physintlag.sq + urban.pct + rentierstate + taxstate + n.events.pre + unscheduled_election + regional_success_lag,
                                ziformula=~.,
                                data = nelda2.sub %>% filter(inc.lose == "0"),
                                family=truncated_nbinom2)

@@

Moving to the hurdle models of post-election protest, we do not observe much of a relationship between overall election integrity and protest. There is no statistically significant relationship between election integrity and protest occurrence in Model 2. Neither is there any significant relationship in interaction with the winner's vote-share, as shown in Figure \@ref(fig:b-protests-margin).

In the corresponding results for the number of post-election protests, there is similarly muted evidence for a connection between the overall level of manipulation and protest risk to incumbents. There is no significant difference between the marginal effect of common levels of election integrity on the number of post-election protests for typical cases across any margin of victory (Figure \@ref(fig:n-protests-margin)). As a whole, the results are in accordance with the theory proposed in the main paper. There is no consistent evidence that lower-quality elections are associated with either a higher risk of protest initiation, or with a larger number of post-election protests.

```{r zero-model-table-fulldv, echo=FALSE, results='asis', warning=FALSE}

models <- list()
#models[['Model XXa']] <- model.n.base2.elfr
models[['Model 10']] <- model.n.base2.elfr
models[['Model 11']] <- model.n.griev.elfr
models[['Model 12']] <- model.size.base2.elfr
models[['Model 13']] <- model.size.griev.elfr

t7 <-  huxreg(models, tidy_args = c("component" = "cond"), borders = 0, number_format = 2,
 statistics = character(0), coefs = c("Intercept" = "(Intercept)", "Electoral integrity" = "v2xel_frefair", "Incumbent vote-share" = "winner.share.upd", "GDP growth (lag)" = "gdpgro.1lag", "Electoral integrity:Incumbent vote-share" = "v2xel_frefair:winner.share.upd",  "Election integrity : GDP growth (lag)" = "gdpgro.1lag:v2xel_frefair")) %>% set_caption("Conditional hurlde models of protest number and size") %>% insert_row("", "Number", "", "Size", "", after = 0)
theme_compact(t7, header_rows = TRUE, header_cols = FALSE) %>% insert_row("Controls", "Yes", "Yes", "Yes", "Yes", after = 14) %>% set_bottom_border(14, everywhere)

@@

@@

### 2023-07-01 Scripts/data_cleaning_massmob.Rmd
Copyedits to appendix (e.g. shortening tables)

Cleaning nelda variables--this will have to be done for all used variables
```{r}
nelda <- nelda %>% dplyr::rename(first.mp.election = nelda2)
nelda <- nelda %>% rename(protests = nelda9)
nelda <- nelda %>% rename(inc.fav.cancel = nelda34)
nelda <- nelda %>% rename(inc.lose = nelda24)
nelda <- nelda %>% rename(inc.termlimit = nelda8)
nelda <- nelda %>% rename(econ.crisis.nelda = nelda18)
nelda <- nelda %>% rename(opp.votegain = nelda7)
nelda <- nelda %>% rename(nelda.protests.fraud = nelda30)
nelda <- nelda %>% rename(new.elections.held = nelda37)
nelda <- nelda %>% rename(inc.replaced.prot = nelda41)
nelda <- nelda %>% rename(preelection_concerns = nelda11)
nelda <- nelda %>% rename(harass_opp = nelda15)
nelda <- nelda %>% rename(opp_leaders_prevented = nelda13)

@@

nelda_massmob <- nelda_massmob %>% filter(is.na(protest_mdy) == T | protest_mdy < election_mdy | (protest_mdy >= election_mdy & str_detect(notes_massmob, regex(pattern = "election*|vot*|ballot*", ignore_case = T))))
```

@@

```{r}
write.csv(nelda_complete, here::here("Data", "nelda_complete.csv"))
```

>>>>

Cleaning nelda variables--this will have to be done for all used variables
```{r}
nelda <- nelda %>% dplyr::rename(first.mp.election = nelda2)
nelda <- nelda %>% rename(unscheduled_election = nelda6)
nelda <- nelda %>% rename(protests = nelda9)
nelda <- nelda %>% rename(inc.fav.cancel = nelda34)
nelda <- nelda %>% rename(inc.lose = nelda24)
nelda <- nelda %>% rename(inc.termlimit = nelda8)
nelda <- nelda %>% rename(econ.crisis.nelda = nelda18)
nelda <- nelda %>% rename(opp.votegain = nelda7)
nelda <- nelda %>% rename(nelda.protests.fraud = nelda30)
nelda <- nelda %>% rename(new.elections.held = nelda37)
nelda <- nelda %>% rename(inc.replaced.prot = nelda41)
nelda <- nelda %>% rename(preelection_concerns = nelda11)
nelda <- nelda %>% rename(harass_opp = nelda15)
nelda <- nelda %>% rename(opp_leaders_prevented = nelda13)

@@

#nelda_massmob <- nelda_massmob %>% filter(is.na(protest_mdy) == T | protest_mdy < election_mdy | (protest_mdy >= election_mdy & str_detect(notes_massmob, regex(pattern = "election*|vot*|ballot*", ignore_case = T)))) #Turn this on to focus only on protests related to the election
```

@@

```{r}
write.csv(nelda_complete, here::here("Data", "nelda_massmob_all.csv")) #File that only looks at election-related massmob was called nelda_complete
```
